Improving phase-matching of FWM with temperature

### 2015-09-18 latex/article.tex
big changes: comsol, mainly but also phasematch

\section{Non-linear optics}
A nonlinear dielectric medium is characterized by a nonlinear relation between \textbf{P} and \textbf{E}, such as
\begin{equation}
	\textbf{P} = \varepsilon_0 \left( \chi^{(1)} \cdot \textbf{E} + \chi^{(2)} : \textbf{E}^2 + \chi^{(3)} \vdots \textbf{E}^3 + \cdots \right) = \textbf{P}_L + \textbf{P}_{NL}
	\label{eq_P_general}
\end{equation}
which originates from the behaviour of bound electrons.

@@

Substituting Eq. (\ref{eq_P_NL}) in Eq. (\ref{eq_E}) we obtain $8^3=512$ terms.
We can then write the non linear terms $P_{NL}$ of the induced electric polarization as
\begin{equation}
	\textbf{P} = \frac{1}{2}\hat{x} \sum_{j=1}^4 P_j \mathrm{exp}[i(\beta_j z - \omega_j t)] + c.c.
	\label{eq_P}
\end{equation}

Replacing \ref{} in Eq. (\ref{eq_helm_P}) leads to eight coupled equation: four of them are equivalent of Eq. (\ref{eq_wg_a}) and describe the field distribution of the mode of each wave.
The latter four are the equivalent of Eq. (\ref{eq_wg_b}) and describe how the field change while travelling through the waveguide.

considering $E_j(\textbf{r}) = F_j(x,y)A_j(z)$ where $F_j$ is the spatial distribution of the mode

@@

where

\begin{equation}
	f_{ij} = \frac{\langle |F_i|^2 |F_j|^2 \rangle}{\sqrt{\langle |F_i|^2 \rangle\langle |F_j|^2 \rangle}}
\end{equation}
and
\begin{equation}
	f_{ijkl} = \frac{\langle F_i^* F_j^* F_k F_l \rangle}{\sqrt{\langle |F_i|^2 \rangle\langle |F_j|^2 \rangle\langle |F_k|^2 \rangle\langle |F_l|^2 \rangle}}
\end{equation}

@@

These equations can be solved introducing $B_j = A_j \,\mathrm{exp}[-2\mathrm{i}\gamma(P_1+P_2)z]$ for $j=3,4$ giving their general solution as
\begin{equation*}
	B_j(z) = (a_j\mathrm{e}^{gz}+b_j\mathrm{e}^{-gz})\mathrm{exp}(-i\kappa z/2)
\end{equation*}
with $\kappa = \Delta + \gamma(P_1 + P_2)$ \textit{effective phase mismatch} and $g = \sqrt{4\gamma^2P_1P_2 - \kappa^2/4}$ the \textit{parametric gain}.

@@

@@

\subsection{Heater configurations}
In order to achieve a greater effect from the different temperature, we tried to move the heater from over the center of the core to the side.
This operation was intended to increase the difference of behaviour between low and high orders.
\subsection{Different geometries}

>>>>

\section{Non-linear optics}
A nonlinear dielectric medium is characterized by a nonlinear relation between \textbf{P} and \textbf{E}, such as
\begin{equation}
	\textbf{P} = \varepsilon_0 \left( \chi^{(1)} \cdot \textbf{E} + \chi^{(2)} : \textbf{E}^2 + \chi^{(3)} \vdots \textbf{E}^3 + \cdots \right) = \mathrm{\textbf{P}_L} + \mathrm{\textbf{P}_{NL}}
	\label{eq_P_general}
\end{equation}
which originates from the behaviour of bound electrons.

@@

Substituting Eq. (\ref{eq_P_NL}) in Eq. (\ref{eq_E}) we obtain $8^3=512$ terms.
We can then write the non linear terms $\mathrm{\textbf{P}_{NL}}$ of the induced electric polarization as
\begin{equation}
	\mathrm{\textbf{P}_{NL}} = \frac{1}{2}\hat{x} \sum_{j=1}^4 P_j \mathrm{exp}[i(\beta_j z - \omega_j t)] + c.c.
	\label{eq_P}
\end{equation}

where for example $P_4$ would be
\[
\begin{array}{rl}
	P_4 &= \frac{3\varepsilon_0}{4} \chi^3_{xxxx}\left[ |\mathrm{E}_4|^2\mathrm{E}_4 2(|\mathrm{E}_1|^2+|\mathrm{E}_2|^2+|\mathrm{E}_3|^2)\mathrm{E}_4 \right. \\
	&+ \left. 2\mathrm{E}_1\mathrm{E}_2\mathrm{E}_3\mathrm{e}^{i\phi_+}+2\mathrm{E}_1\mathrm{E}_2\mathrm{E}_3^*\mathrm{e}^{i\phi_-}\right] \\

\end{array}
\]
\hspace{18pt}with $\phi_+$ and $\phi_-$ defined as
\[
\begin{array}{lr}
\phi_+ &= (\beta_1+\beta_2+\beta_3-\beta_4+)z - (\omega_1+\omega_2+\omega_3-\omega_4)t \\
\phi_- &= (\beta_1+\beta_2-\beta_3-\beta_4+)z - (\omega_1+\omega_2-\omega_3-\omega_4)t \\
\end{array}
\]

Replacing Eq. (\ref{eq_P}) in Helmholtz equation (\ref{eq_helm_P}) leads to eight coupled equations: four of them are equivalent of Eq. (\ref{eq_wg_a}) and describe the field distribution of the mode of each wave.
The remaining four are the equivalent of Eq. (\ref{eq_wg_b}) and describe how the field change while travelling through the waveguide.
Those, considering $E_j(\textbf{r}) = F_j(x,y)A_j(z)$ where $F_j$ is the spatial distribution of the mode, can be written as:

@@

where
\begin{equation}
	f_{ij} = \frac{\langle |F_i|^2 |F_j|^2 \rangle}{\sqrt{\langle |F_i|^2 \rangle\langle |F_j|^2 \rangle}}
\end{equation}
\hspace{18pt}and
\begin{equation}
	f_{ijkl} = \frac{\langle F_i^* F_j^* F_k F_l \rangle}{\sqrt{\langle |F_i|^2 \rangle\langle |F_j|^2 \rangle\langle |F_k|^2 \rangle\langle |F_l|^2 \rangle}}
\end{equation}
\hspace{18pt}are the overlap integrals of the different modes, where the brackets mean an integration on a plane $\langle g(x,y)\rangle = \int\int_{-\inf}^{\inf}g(x,y)\mathrm{dxdy}$.
The physical interpretation of such quantities is how much different modes are superimposed/\ref{}/overlapped with each others.

@@

These equations can be solved introducing $B_j = A_j \,\mathrm{exp}[-2\mathrm{i}\gamma(P_1+P_2)z]$ for $j=3,4$ giving their general solution as
\begin{equation*}
	B_j(z) = (a_j\mathrm{e}^{gz}+b_j\mathrm{e}^{-gz})\mathrm{exp}(-i\kappa z/2)
\end{equation*}
with $\kappa = \Delta k + \gamma(P_1 + P_2)$ \textit{effective phase mismatch} and $g = \sqrt{4\gamma^2P_1P_2 - \kappa^2/4}$ the \textit{parametric gain}.

@@

We can define a length scale, known as the coherence length, using $L_{coh} = 2\pi/|\Delta\kappa|$, where $\Delta\kappa$ is the maximum value of the effective phase mismatch that can be tolerated.
Moreover significant FWM occurs if $L_{sam}<L_{coh}$ where $L_{sam}$ is the sample length.

@@

\subsection{Heater configurations}
In order to achieve a greater effect from the different temperature, we tried to move the heater from over the center of the core to the side.
This operation was intended to increase the difference of behaviour between low and high orders enabling thus the creation of new peaks in the coherence length.
\subsection{Different geometries}
